\textls[-0]{\thetitle}

### 2023-02-08 introduction.tex
fix typos and awkward wordings

\noindentparagraph{Contributions}

@@

Integrating family polymorphism into a dependent type theory for
logical reasoning, however, poses significant technical challenges.
As we analyze, pillars of dependent type theories—including
inductive types, definitional equality, and logical consistency—are
all inimical to the kind of extensibility and family polymorphism
found in existing OO language designs.
Thus, our contributions include novel design recipes for dealing with
these challenges and strong meta\-theoretical guarantees on the
underlying logic.
%
Specifically, we make the following contributions.

>>>>

\noindentparagraph{Contributions.}

@@

Integrating family polymorphism into a dependent type theory for
logical reasoning, however, poses significant technical challenges.
As we analyze, pillars of dependent type theories—including
inductive types, definitional equality, and logical consistency—are
all inimical to the kind of extensibility and family polymorphism
found in existing OO language designs.
Thus, our contributions include novel design recipes for dealing with
these challenges and foundational meta\-theoretical guarantees on the
underlying logic.
%
Specifically, we make the following contributions.

### 2023-02-08 metatheory-condensed.tex
fix typos and awkward wordings

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
For readability, we feel free to use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and feel free to write its type~$A_i$, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

>>>>

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
For readability, we use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and write its type~$A_i$, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

### 2023-02-08 related-work.tex
add related work
fix typos and awkward wordings

The design pattern \emph{data types à la carte} (DTC) introduced for Haskell by~\citet{dtc}
is a source of inspiration for many approaches
\cite{delaware2013,delaware2013b,schwaab2013modular,keuchel2013generic,forsta2020}.
The original DTC encoding requires type-level general recursion that
fails the strict positivity check imposed by proof assistants including Coq and Agda.
\citet{delaware2013} introduce \emph{meta-theory à la carte} (MTC):
it overcomes the problem by using Church encodings for
data types and using Mendler-style folds for evaluation,
though it requires \lsti{Set} impredicativity.
Feature composition is automated through heavy use of type classes.
The framework is implemented as a Coq library.
\citet{schwaab2013modular} adapt DTC to Agda by considering a restricted
class of functors that admit least fixed points.
\citet{keuchel2013generic} use datatype-generic programming techniques
for the underlying representation of type-level fixed points and
avoid \lsti{Set} impredicativity.

@@

On the other hand, the extra\-linguistic nature of the approaches tend
to lead to non-idiomatic code and offset their user-friendliness.
In particular, because data types have to be encoded (rather than expressed
through natively supported inductive types), the resulting code is
less readable and the resulting programming style inaccessible to non-experts.
In addition, extra programmer effort may be required, such as
having to manually prove additional well-formedness conditions. %on the algebras\EDJ{What is this `algebra'? I mean if it is a very frequent word to the audience  familiar with DTC then removing explanation is fine.}.

>>>>

The design pattern \emph{data types à la carte} (DTC) introduced for Haskell by~\citet{dtc}
is a source of inspiration for many approaches
\cite{delaware2013,delaware2013b,schwaab2013modular,keuchel2013generic,forsta2020}.
%\cite{vdr2022intrinsically}
The original DTC encoding requires type-level general recursion that
fails the strict positivity check imposed by proof assistants including Coq and Agda.
\citet{delaware2013} introduce \emph{meta-theory à la carte} (MTC):
it overcomes the problem by using Church encodings for
data types and using Mendler-style folds for evaluation,
though it requires \lsti{Set} impredicativity.
Feature composition is automated through heavy use of type classes.
The framework is implemented as a Coq library.
\citet{schwaab2013modular} adapt DTC to Agda by considering a restricted
class of functors that admit least fixed points.
\citet{keuchel2013generic} use datatype-generic programming techniques
for the underlying representation of type-level fixed points and
avoid \lsti{Set} impredicativity.

@@

On the other hand, the extra\-linguistic nature of the approaches tend
to lead to non-idiomatic code and offset their user-friendliness.
In particular, because data types have to be encoded (rather than expressed
through natively supported inductive types), the resulting code can be
obtuse at first blush, making the programming style inaccessible to non-experts.
In addition, extra programmer effort may be required, such as
having to manually prove additional well-formedness conditions. %on the algebras\EDJ{What is this `algebra'? I mean if it is a very frequent word to the audience  familiar with DTC then removing explanation is fine.}.
